Project 4

### 2018-11-17 Project4/report/ms.tex
Updates from ShareLaTeX

\section{Introduction}
\label{sec:introduction}
Studying the phase trans

@@

\section{Results}
\label{sec:results}

>>>>

\section{Introduction}
\label{sec:introduction}
To study the phase transitions in a magnetic system we consider the Ising model for a system of finite lattice size. The energy of the system, by the Ising model, is 
%
\begin{gather*}
    E = -J\sum_{< kl >}^N s_k s_l,
\end{gather*}
%
when there is no external magnetic field applied to the system. For solving this system we consider the Metropolis algorithm, which is a Markov chain Monte Carlo method.

@@

\section{Results}
\label{sec:results}
\begin{figure}[t]

c)
\begin{figure}
\mbox{\epsfig{figure=EofMCC-GS-T1-L20-1e5.pdf,width=\linewidth,clip=}}
\caption{text}
\label{fig:E(mcc)T1}
\end{figure}

\begin{figure}
\mbox{\epsfig{figure=EofMCC-GS-T1-L20-1e5.pdf,width=\linewidth,clip=}}
\caption{text}
\label{fig:E(mcc)T1}
\end{figure}

\begin{figure}
\mbox{\epsfig{figure=EofMCC-GS-T1-L20-1e5.pdf,width=\linewidth,clip=}}
\caption{text}
\label{fig:E(mcc)T1}
\end{figure}

\begin{figure}
\mbox{\epsfig{figure=EofMCC-GS-T1-L20-1e5.pdf,width=\linewidth,clip=}}
\caption{text}
\label{fig:E(mcc)T1}
\end{figure}

\begin{figure}
\mbox{\epsfig{figure=EofMCC-GS-T1-L20-1e5.pdf,width=\linewidth,clip=}}
\caption{text}
\label{fig:E(mcc)T1}
\end{figure}

\begin{figure}
\mbox{\epsfig{figure=EofMCC-GS-T1-L20-1e5.pdf,width=\linewidth,clip=}}
\caption{text}
\label{fig:E(mcc)T1}
\end{figure}

MofMCC-GS-T1-L20-1e5.pdf

EofMCC-GS-T2_4-L20-1e5.pdf
MofMCC-GS-T2_4-L20-1e5.pdf

EofMCC-T1-L20-1e6.pdf
MofMCC-T1-L20-1e6.pdf

EofMCC-T2_4-L20-1e6.pdf
MofMCC-T2_4-L20-1e6.pdf

accepts_of_T-T1T2_4-L20.pdf
accepts-T1T2_4-L20-1e5.pdf
CV-T2-23.pdf
CV-T22-24.pdf
E-T2-23.pdf
E-T22-24.pdf
FittedTc.pdf
M-T2-23.pdf
M-T22-24.pdf
PE-T1-L20-1e6.pdf
PE-T2_4-L20-1e6.pdf
X-T2-23.pdf
X-T22-24.pdf

\begin{figure}
\mbox{\epsfig{figure=,width=\linewidth,clip=}}
\caption{text}
\label{fig:figure_label}
\end{figure}
